A Fast Unified Model for Parsing and Sentence Understanding

### 2016-05-27 writing/hard_stack_paper/paper.tex
First awkward stab at lengthier thin stack explanation

We propose an alternative space-efficient stack representation inspired by the zipper technique \citep{huet1997zipper}, that we call \textit{thin stack}. For each input sentence, we represent the stack with a single $T \times D$ matrix $S$. Each row $S_t$ represents the top of the actual stack at timestep $t$. We maintain a queue of backpointers into $S$ that indicates which elements would be involved in a \reduce\ operation at any given step. Algorithm~\ref{alg:thin-stack} describes the full mechanics of a stack feedforward in this compressed representation. It operates on the single $T \times D$ matrix $S$ and a backpointer queue $Q$. Table~\ref{tbl:thin-stack} shows an example run.

>>>>

We propose an alternative space-efficient stack representation inspired by the zipper technique \citep{huet1997zipper}, that we call \textit{thin stack}. For each input sentence, we represent the stack with a single $T \times D$ matrix $S$. Each row $S_t$ represents the top of the actual stack at timestep $t$. At each timestep we can \shift\ a new element onto the stack, or \reduce\ the top two elements of the stack into a single element. To shift an element from the buffer to the top of the stack at timestep $t$, we simply write it into the location $S[t]$. We maintain a queue $Q$ of pointers into $S$ which contains the row indices of $S$ which are still present in the actual stack. To retrieve the top two elements of the stack, we look up the two rows indicated by the final two elements of the queue $Q$. These retrieved rows are used to perform the \reduce\ operation, which modifies $Q$ to mark that some rows of $S$ have now been replaced in the actual stack. Algorithm~\ref{alg:thin-stack} describes the full mechanics of a stack feedforward in this compressed representation. It operates on the single $T \times D$ matrix $S$ and a backpointer queue $Q$. Table~\ref{tbl:thin-stack} shows an example run.
